\documentclass{article}

\usepackage{titlesec}
\usepackage{titling}
\usepackage[margin=1in]{geometry}


\titleformat{\section}
{\huge\bfseries}
{}
{0cm}
{}[\titlerule]

\titleformat{\subsection}
{\bfseries}
{}
{0cm}
{}

\titleformat{\subsubsection}[runin]
{\bfseries}
{}
{0cm}
{}[---]

\renewcommand{\maketitle}{
\begin{center}
	{\huge\bfseries
	\theauthor}

\vspace*{1cm}
vitominheere@gmail.com

\end{center}
}

\begin{document}

\author{Vito Minheere}


\maketitle

\section{\sc Profile}
Eager Data Engineer with 3+ years of experience, mainly in \emph{Python} and \emph{Google Cloud Platform}. Interested in building the simplest and most effienct solution to data problems. \\
Experience in data and software engineering allows me to streamline the transformed data to cater to developers and end-users.

\section{\sc Job experience}
\subsection{Data Engineer - Qlouder/Cloud Technology Solutions, Utrecht} \hfill {\em 04-2019} \\
Work as a Data Engineering consultant in the Google Cloud Platform ecosystem \\
Build modern web applications with \emph{Python} but also worked with \emph{Java}, \emph{TypeScript}, \emph{SQL} and \emph{NoSQL} databases. \\ 
Build Data Pipelines using \emph{Google Cloud Platform} tools. \\
Develop microservices using \emph{Docker}, \emph{Kubernetes}, \emph{Terraform} \\

\subsection{Data Engineer - Energyworx, Houten} \hfill {\em 05-2018 04-2019} \\
Inhouse engineer working on data ingestion with \emph{Apache Kafka} and transformation. \\
Managed the migration of the largest US customer to the new version of the data analysis framework \\
Build business rules with \emph{Pandas} and \emph{Scikit Learn} \\ 
Provide support to custom customer code within the platform. \\

\subsection{Graduation Internship - Globalistics, Valencia} \hfill {\em 09-2017 03-2018} \\
Extraction, transformation and loading (ETL) of data gathered via API \\
Use gathered data in modelling to predict shipping prices \\
Build API with \emph{Django} to show results on website \\


\subsection{Backend Developer - Nfnty/Conneqtech, Vlissingen} \hfill {\em 08-2016 09-2017} \\
Worked on multiple client projects, both frontend and backend. \\
Build API in \emph{PHP} and frontend in \emph{AngularJS}. \\
Designed solutions for issues raies in ticket system. \\

\section{Certifications}
\subsection{Google Cloud Professional Data Engineer}\hfill {\em 06-2020 06-2022} \\

\section{Projects}
\subsection{Data Extraction - Greenhouse}
Extract data from internal applications and appliances for ingestion into databases and Cloud Storage. Build with \emph{Python} and \emph{Cloud Functions}

\subsection{Accounting Tool - Tourism}
Use data from the Datalake to be able to generate price quotes based on prediction data. Build the calculation backend in \emph{NodeJS} and \emph{Typescript}, frontend was done in \emph{Angular}.

\subsection{Datalake - Tourism}
Extract and transform data from multiple sources to a single datalake. Datalake is used to feed dashboards, spreadsheets and internal applications. Ingestion framework build with \emph{Python} using \emph{BigQuery} and \emph{AppEngine} \\
Exporting data to spreadsheets allowed company to work on them simultaneously in the cloud. \\ 

\subsection{Data Processing - Utilities}
Refactoring the monolith class for transforming data into smaller, easier unit-testable components \\
Analyzing and transforming time series data from IoT smart meters using Pandas and Numpy \\
Supporting customers with updating and applying business rules to their data sources \\

\subsection{Data Science - Container Shipping}
Research into container transportation price models \\
Enriching API data from suppliers with extra data to be used in model \\
Comparing the performance and accuracy of different models with \emph{Scikit-learn} \\
Building an API with \emph{Django} to enable the product owner's website to query actual and predicted container transport prizes \\

\clearpage

\section{Education}
\subsection{Bachelor Software Engineering}\hfill {\em 2013-2018} \\
Minor in Data Science
\subsection{MBO Network Administrator}\hfill {\em 2009-2013} \\

\section{Technical Skills}
{\sl \textbf{Programming Languages:}} Python, Bash, Typescript \\
{\sl \textbf{Data Technologies:}} Pandas, BigQuery, Dataflow \\
{\sl \textbf{Operations Technologies:}} Docker, Terraform, Git \\
{\sl \textbf{Web Backend Technologies:}} Firebase, Django, Flask, Dart, REST \\
{\sl \textbf{Web Frontend Technologies:}} Flutter, Angular \\
\end{document}
